---
title: "hand_crafted_bayesian_network_example"
author: "Aditya Ponnada"
date: "4/20/2021"
output: html_document
---

## include libraries
```{r}

library(DAAG)
library(bnlearn)
library(ggplot2)
library(visNetwork)
library(catnet)
library(igraph)

```

## Test function to insert missingness in the dataframe
```{r}
insert_missing_data <- function(df){
  df <- as.data.frame(lapply(df, function(cc) cc[ sample(c(TRUE, NA), prob = c(0.50, 0.50), size = length(cc), replace = TRUE) ]))
  return (df)
}
```


## load and plot sample data
```{r}

ais = DAAG::ais

ais <- insert_missing_data(ais)

ggplot(ais, aes(x = sport, y = hg, fill = sport)) + geom_boxplot()

```

## Start by using discrete case for simplicity
We first convert the continious variables into categorical variables
```{r}
# set boolean variables
ais$high_hc <- as.factor(ais$hc > median(ais$hc, na.rm = TRUE))
ais$high_hg <- as.factor(ais$hg > median(ais$hg, na.rm = TRUE))

# create an empty graph
structure <- empty.graph(c("high_hc", "high_hg", "sport"))

# set relationships manually
modelstring(structure) <- "[high_hc][sport][high_hg|sport:high_hc]"


```

## Plot the network structure
```{r}

plot.network <- function(structure, ht = "400px"){
  nodes.uniq <- unique(c(structure$arcs[,1], structure$arcs[,2]))
  nodes <- data.frame(id = nodes.uniq,
                      label = nodes.uniq,
                      color = "darkturquoise",
                      shadow = TRUE)
  edges <- data.frame(from = structure$arcs[,1],
                      to = structure$arcs[,2],
                      arrows = "to",
                      smooth = TRUE,
                      shadow = TRUE,
                      color = "black")
  return(visNetwork(nodes, edges, height = ht, width = "100%"))
}

```

Try the plot
```{r}

# observe structure
plot.network(structure)


```

## Model output and conditional probabilities
```{r}

ais.sub <- ais[ais$sport %in% c("Netball", "Tennis", "W_Polo"), c("high_hc", "high_hg", "sport")]
ais.sub$sport <- factor(ais.sub$sport)
bn.mod <- bn.fit(structure, data = ais.sub)
bn.mod


```

## Some test queries to try out
```{r}

cat("P(high hemaglobin levels) =", cpquery(bn.mod, (high_hg=="TRUE"), TRUE), "\n") ## Why is TRUE passed as a default here??

cat("P(high hemaglobin levels | play water polo and have high hematocrit ratio) =", cpquery(bn.mod, (high_hg=="TRUE"), (sport == "W_Polo" & high_hc == "TRUE")), "\n")

```

## Example query to check probability
With the same model we can query the probability that an athlete plays water polo given we observe their high hemoglobin levels or the probability of having high hemoglobin levels given they play water polo.
```{r}

cat("P(Plays water polo | High HG and High HC) = " , cpquery(bn.mod, (sport == "W_Polo"), (high_hg == "TRUE" & high_hc == "TRUE")), "\n")


```

But if we did not know the hc ratio, we can sum over all the prob of hc within the cpquery
```{r}

cat("P(high hemaglobin levels | play water polo) =", cpquery(bn.mod, (high_hg=="TRUE"), (sport == "W_Polo")), "\n")

```

## try the same example with the continious case
```{r}

# create an empty graph
structure <- empty.graph(c("hc", "hg", "sport"))
# set relationships manually
modelstring(structure) <- "[hc][sport][hg|sport:hc]"
# subset and fit
ais.sub <- ais[ais$sport %in% c("Netball", "Tennis", "W_Polo"), c("hc", "hg", "sport")]
ais.sub$sport <- factor(ais.sub$sport)
bn.mod <- bn.fit(structure, data = ais.sub)
bn.mod

```

## Query the continious data bn.mod model
```{r}

cat("P(hemaglobin levels > 14 | play water polo and have high hematocrit ratio) =", cpquery(bn.mod, (hg > 14), (sport == "W_Polo" & hc > 42 )), "\n")

```

## Getting chained relationships
Adding lean body mass to the equation
```{r}

# create an empty graph
structure <- empty.graph(c("hc", "hg", "sport", "lbm"))
# set relationships manually
modelstring(structure) <- "[lbm][hc|lbm][sport][hg|sport:hc]"
plot.network(structure)
# subset and fit
ais.sub <- ais[ais$sport %in% c("Netball", "Tennis", "W_Polo"), c("hc", "hg", "sport", "lbm")]
ais.sub$sport <- factor(ais.sub$sport)
bn.mod <- bn.fit(structure, data = ais.sub)
bn.mod

```

## Determine network structure algorithmicly
More suitable for large cases --> large number of samples? or large number of variables in the network? --> but more hand crafted relationships can be inserted into the structure to inform it better. Does not seem to work with missing data? Impute??

```{r}

# learn the structure using the hill climbing algorithm and the BIC
structure <- hc(ais.sub, score = "bic-cg")
plot.network(structure)

```

## Model fit based on the algorithm derived structure
```{r}
bn.mod <- bn.fit(structure, data = ais.sub)
cat("P(hemaglobin levels > 14 | play water polo and have LBM > 65 kg) =", cpquery(bn.mod, (hg > 14), (sport == "W_Polo" & lbm > 65 )), "\n")
```

## Fitting the full model
Including all the variables after accounting for multi-colinearity
```{r}

ais.sub <- ais[, c("hc", "hg", "sport", "lbm", "rcc", "wcc", "ferr", "ht", "wt", "sex", "ssf")]
structure <- hc(ais.sub, score = "bic-cg")
bn.mod <- bn.fit(structure, data = ais.sub)
plot.network(structure, ht = "600px")

```

# Trying with catnet package
```{r}

## Create a copy of the dataframe

ais_v2 = ais
```

## Generating a network with hc, hg, and sport variables
```{r}
keep <- c("sport", "high_hc", "high_hg")

ais_v2.sub <- ais_v2[, keep]

```

Generate the network structure using the subset
```{r}

cnet <- catnet::cnNew(
  nodes = c("sport", "high_hc", "high_hg"),
  cats = list(c("1","2"), c("1","2"), c("1","2")),
  parents = list(c(3), c(3), NULL)
)

```

## Setting the emperical probabilities
```{r}

cnet2 <- catnet::cnSetProb(cnet, data=ais_v2.sub)

```

## Plot and query the network
```{r}
catnet::cnProb(cnet2,which='high_hg')

Sys.setenv(R_CATNET_USE_IGRAPH=TRUE)

cnPlot(cnet2)

```

## Custom plot for catnetwork
```{r}

plotAdj <- function(object, ...){
    nodes = cnNodes(object)
    l = length(nodes)
    parents = object@parents
    adj = matrix(0, ncol=l, nrow=l, dimnames = list(nodes, nodes))
    for(i in seq_along(parents)){
      adj[i, parents[[i]]] = 1
    }
    g = igraph::graph_from_adjacency_matrix(adj)
    plot(g, ...)
    invisible(adj)
}

```


## Testing the plot
```{r}

plotAdj(cnet2, vertex.color="lightblue")

```


## Query different attributes of cnet2
```{r}

cnNumNodes(cnet2)
cnEdges(cnet2)

cnPlotProb(cnet2)

cnComplexity(cnet2)

dag2cpdag(cnet2)

```


## Testing generating a random network with CatNet
```{r}

set.seed(123)
cnet3 <- catnet::cnRandomCatnet(numnodes = 3, maxParents = 2, numCategories = 2)

```

## simulated annealing in catnet
```{r}
# netlist1 = cnSearchSA(ais_v2.sub, maxParentSet = 2)
netlist1 = cnSearchSA(ais_v2.sub)
```

## find the best estimate
```{r}
catnet.best = cnFindBIC(netlist1, nrow(ais_v2.sub))

```

## Check the best network
```{r}

plotAdj(catnet.best, vertex.color="lightblue")

dag2cpdag(catnet.best)

```



## Try catnet with other example
```{r}

rm(list=ls())

### generate random data (not simply independent binomials)
set.seed(123)
n.obs <- 10
a1 <- rbinom(n.obs,1,.3)
a2 <- runif(n.obs)
a3 <- floor(-3*log(.25+3*a2/4))
a3[a3>=2] <- NA
a2 <- floor(2*a2)
my.data <- data.frame(a1,a2,a3 )
### discretize data into proper categories
my.data <- cnDiscretize(my.data,numCategories=2)

my.data

## say we want a2 conditional on a1,a3

## first generate a network with a1,a3 ->a2
cnet <- cnNew(
      nodes = c("a1", "a2", "a3"),
      cats = list(c("1","2"), c("1","2"), c("1","2")),
      parents = list(NULL, c(1,3), NULL)
      )


## set the empirical probabilities from data=my.data
cnet2 <- cnSetProb(cnet,data=my.data)

## to get the conditional probability table
cnProb(cnet2,which='a2')


```

## Plot this dummy cnet
```{r}
Sys.setenv(R_CATNET_USE_IGRAPH=TRUE)
catnet::cnPlot(cnet2)
```

