---
title: "parse_EOD_data"
author: "Aditya Ponnada"
date: "5/27/2021"
output: html_document
---

## Import libraries
```{r}
library(psych)
library(dplyr)
library(plyr)
library(reshape2)

```

## Read and combine the csv files for EOD
```{r}
pre_process_root_path = "D:/new_data_pre_processed/ema_promptresponse/"

# file_pattern <- paste0(pre_process_root_path, '/*/phone_promptresponse_clean_*.csv')
file_pattern <- paste0(pre_process_root_path, '/*@timestudy_com.csv')
```

## Combine and read all the files for EMA
```{r}

pattern_files_found <- Sys.glob(file_pattern)

# list_of_files <- list.files(pattern_files_found, recursive = TRUE, full.names = TRUE)
list_of_files <- list.files(path = pre_process_root_path, pattern = NULL, full.names = TRUE)

# combined_uema_file <- do.call(plyr::rbind.fill(), lapply(pattern_files_found, read.csv))
combined_ema_file <- ldply(list_of_files, read.csv, header = TRUE, na.strings = c("", "NA"))

```


## Filter out daily prompts on TIME days
```{r}

combined_ema_time_daily_df <- subset(combined_ema_file, combined_ema_file$Prompt_Type == "Daily" & combined_ema_file$Study_Mode == "TIME")

```

## Filter out never started or neverprompted prompts
```{r}
include_status <- c("Started", "Completed", "PartiallyCompleted")
combined_ema_time_daily_df <- subset(combined_ema_time_daily_df, combined_ema_time_daily_df$Answer_Status %in% include_status)
```


## Filter out unwanted columns
```{r}

combined_ema_time_daily_df <- combined_ema_time_daily_df[, c(1:109)]

```

## get column pair lists
```{r}
question_column_set_list <- names(combined_ema_time_daily_df[, c(34:109)])
```

First describe the set types:
Question ID columns 1, 5, ... i = 1, i + 4
Question_text columns, 2, 6, ... i = 2, i + 4
Answer_text columns, 3, 7 ... i = 3, i + 4
Answer_time columns, 4, 8, ... i = 4, i + 4
```{r}

get_column_type_list <- function(start_index, col_list){
  
  type_list <- c()
  num_iters <- length(col_list)/4
  for (i in 1:num_iters){
    type_list <- c(type_list, col_list[[start_index]])
    start_index = start_index + 4
    
  }
  
  return(type_list)
  
}

```

## Get type lists
```{r}
Q_ID_cols <- get_column_type_list(1, question_column_set_list)
Q_text_cols <- get_column_type_list(2, question_column_set_list)
ans_text_cols <- get_column_type_list(3, question_column_set_list)
ans_time_cols <- get_column_type_list(4, question_column_set_list)
```

## Convert to long format
```{r}

time_daily_long_df <- reshape(combined_ema_time_daily_df, direction="long", 
        varying=list(Q_ID_cols, Q_text_cols, ans_text_cols, ans_time_cols), 
        v.names=c("Q_D","Q_TEXT","ANS_TEXT", "ANS_TIME"))

```

