---
title: "simple_catnet_examples"
author: "Aditya Ponnada"
date: "4/25/2021"
output: html_document
---


## Include library
```{r}
library(igraph)
library(catnet)
library(graph)
```

## Keep a general catnet plotting function
```{r}
plot_catnet <- function(object, ...){
    nodes = cnNodes(object)
    l = length(nodes)
    parents = object@parents
    adj = matrix(0, ncol=l, nrow=l, dimnames = list(nodes, nodes))
    for(i in seq_along(parents)){
      adj[i, parents[[i]]] = 1
    }
    g = igraph::graph_from_adjacency_matrix(adj)
    plot(g, vertex.frame.color = "black",
         vertex.color = c("lightgoldenrod"), # Node border color
    vertex.shape=c("circle"),
    vertex.size = c(15),
    vertex.label.color = c("black"),
    vertex.label.font = c(1),                        # One of “none”, “circle”, “square”, “csquare”, “rectangle” “crectangle”, “vrectangle”, “pie”, “raster”, or “sphere”
    # vertex.size=c(15:24),                          # Size of the node (default is 15)
    # vertex.size2=NA)
    edge.color=c("black"),           # Edge color
    edge.width=1,                        # Edge width, defaults to 1
    edge.arrow.size=0.5,                           # Arrow size, defaults to 1
    edge.arrow.width=0.5,                          # Arrow width, defaults to 1
    edge.lty=c("solid")
    )
    invisible(adj)
}
```



## Creating new networks
Normally the network is "inferred" from the data and created "implicitly". But sometimes it may be possible to create the network explicitly and manually by the user. Below is one such example. cnNew function creates a new network. The function takes following arguments: a vector of node names (nodes), a list of node categories (cats), a list of parents ((parents)) and an optional list of conditional probabilities (probs). 

```{r}

cnet <- cnNew(
  nodes = c("a", "b", "c"),
  cats = list(c("1","2"), c("1","2"), c("1","2")),
  parents = list(NULL, c(1), c(1,2)),
  probs = list( c(0.2,0.8),
  list(c(0.6,0.4),c(0.4,0.6)),
  list(list(c(0.3,0.7),c(0.7,0.3)),
  list(c(0.9,0.1),c(0.1,0.9)))) )

```

## Test explore the plot
```{r}
plot_catnet(cnet)
```

## Generating a random network
```{r}

# set.seed(123)

cnet1 <- cnRandomCatnet(numnodes = 4, maxParents = 2, numCategories = 2)

plot_catnet(cnet1)

```

## Accessing network attributes and characteristics
```{r}

cnNumNodes(cnet)

cnNodes(cnet)

cnEdges(cnet)

cnParents(cnet)

```

In matrix forms
```{r}

cnMatParents(cnet)

cnMatEdges(cnet)

```

## Complexity of a network
The complexity is an integer number specifying the number of parameters needed to define the probability structure of the network.

```{r}

cnComplexity(cnet)

```

## Topological node order
```{r}


cnOrder(cnet)

```

## Comparing networks
There are two basic criteria for comparing networks. First, a topological one that compares the graphical structure of the networks and second, a probabilistic one, involving the distributions specified by the networks.

```{r}

set.seed(456)
cnet3 <- cnRandomCatnet(cnNumNodes(cnet), maxParents=2, numCategories=2)
cnet3@nodes <- cnet@nodes
cnCompare(object1=cnet, object2=cnet3)

```

## Generating samples + making prediction
```{r}

samples1 <- cnSamples(object=cnet, numsamples = 100, output = "matrix")

dim(samples1)

samples2 <- cnSamples(object=cnet, numsamples = 100, output = "frame")

```

## Trying perturbations
```{r}
samples3 <- cnSamples(object = cnet, numsamples = 10, perturbations = c(0,0,1))
```


## trying predictions
```{r}

## Generate a sample of size 12 and set the last 3 nodes as non-available
numnodes <- cnNumNodes(cnet)
samples4 <- cnSamples(object = cnet, numsamples = 12, output="matrix")
## predict the last three nodes in cnet from the rest
## by setting their values in 'samples3' as NA
samples4[numnodes -2, ] <- rep(NA, 12)
samples4[numnodes - 1, ] <- rep(NA, 12)
samples4[numnodes, ] <- rep(NA, 12)

## predict the values of the last 3 nodes
new_samples <- cnPredict(object = cnet, data = samples4)

```

## learning network from data

Network estimation for given node order

```{r}

set.seed(789)
cnet2 <- cnRandomCatnet(numnodes = 10, maxParents = 2, numCategories = 2)
nodeOrder <- order(runif(cnNumNodes(cnet2)))
cnet2

```

## Show the graph
```{r}

plot_catnet(cnet2)

```

## Generate a sample from cnet structure
```{r}

samples <- cnSamples(object = cnet2, numsamples = 100, output = "frame")

netlist <- cnSearchOrder(data=samples, perturbations = NULL, maxParentSet = 2, maxComplexity = 20, nodeOrder = nodeOrder, parentsPool = NULL, fixedParents = NULL)

```

## find the reconstructed network with the true complexity
```{r}

bnet <- cnFind(netlist, 20)
bnet2 <- cnFindBIC(netlist)

plot_catnet(bnet)
plot_catnet(bnet2)

```

In the next example, we generate a random network with 12 nodes and then search for the best
fitting networks that comply with the following requirements: (1) the last node is not a parent to
anyone else, and (2) the first two nodes are necessarily parents to all of the rest nodes. The search is
restricted to the ’true’ node order, the one of the network from which the data is generated, as obtained
by cnOrder(cnet) function.

```{r}

set.seed(123)
nnodes <- 12
cnet <- cnRandomCatnet(numnodes = nnodes, maxParents = 5, numCategories = 2)
norder <- cnOrder(cnet)

plot_catnet(cnet)


```

Add additional parameters
```{r}

parPool <- vector("list", nnodes)
for (i in 1:nnodes){
  parPool[[i]] <- 1:(nnodes-1)
}

fixParPool <- vector("list", nnodes)
for (i in 3:nnodes){
  fixParPool[[i]] <- c(1,2)
}

samples <- cnSamples(cnet, numsamples = 200)

eval <- cnSearchOrder(data = samples, perturbations = NULL, maxParentSet = 2, maxComplexity = 200, nodeOrder = norder, parentsPool = parPool, fixedParents = fixParPool)

eval

eval_best <- cnFind(eval)

plot_catnet(eval_best)

```

## Network selection with AIC and BIC
```{r}

set.seed(345)

# generate a 100 size sample from cnet6
cnet6 <- cnRandomCatnet(numnodes = 12, maxParents = 5, numCategories = 2)
samples <- cnSamples(object = cnet6, numsamples = 100, output = "matrix")
num_order <- order(runif(1:dim(samples)[1]))
eval <- cnSearchOrder(data = samples, perturbations = NULL, maxParentSet = 2, parentSizes = NULL, maxComplexity = 50, nodeOrder = num_order, parentsPool = NULL, fixedParents = NULL, echo = FALSE)


```

Get a network based on AIC and plot it
```{r}
aic_net <- cnFindAIC(eval)

plot_catnet(aic_net)
```

Get a network based on BIC and plot it
```{r}

bic_net <- cnFindBIC(eval)

plot_catnet(bic_net)

```

## Plot likelihoof vs complexity plots

```{r}

plot(eval@complexity, eval@loglik, xlab="Complexity", ylab = "Log-likelihood", main="Model selection: AIC and BIC complexities in red and blue.")

abline(v=aic_net@complexity,lty=2, col="red")

abline(v=bic_net@complexity,lty=3, col="blue")

```


