---
title: "Explore uEMA trajectories"
author: "Aditya Ponnada"
date: "4/12/2021"
output: html_document
---

# Include libraries
```{r}
library(lubridate)
library(dplyr)
library(plyr)
library(reshape2)
library(plotly)
library(ggplot2)
library(shiny)
library(shinycssloaders)
library(shinydashboard)
library(psych)

```

# Read the combined uEMA response file

Get the root file location and construct user paths from it
```{r}
# pre_process_root_path <- "D:/Intermediate_TIME_files/intermediate_file"
pre_process_root_path <- "D:/new_data_pre_processed/watch"

# file_pattern <- paste0(pre_process_root_path, '/*/*/watch_promptresponse_clean_*.csv')
file_pattern <- paste0(pre_process_root_path, '/*/watch_promptresponse_clean_*.csv')

```


## Combine all the prompt response files for the participant
```{r}
pattern_files_found <- Sys.glob(file_pattern)

combined_uema_file <- do.call(rbind, lapply(pattern_files_found, read.csv))
```

## Read the combined daily report file
```{r}

combined_report_file = paste0('D:/new_data_pre_processed', '/combined_report_N70.csv')
combined_report_df <- read.csv(combined_report_file, header = TRUE, sep = ',')

```

## Convert the prompt time to date time column
For uEMA combined file

```{r}
combined_uema_file <- subset(combined_uema_file, combined_uema_file$Answer_Status == "Completed" | combined_uema_file$Answer_Status == "CompletedThenDismissed" )
combined_uema_file <- subset(combined_uema_file, combined_uema_file$Question_X_Answer_Text != "-NOT_ANS-")

## if unanswered then set prompt time as the completion time?
# combined_uema_file$Prompt_Time_only <- substr(combined_uema_file$Initial_Prompt_Local_Time, 12, 19)
# combined_uema_file$Question_Set_Completion_Local_Time[combined_uema_file$Question_X_Answer_Text == '-NOT_ANS-'] <- combined_uema_file$Prompt_Time_only


combined_uema_file$date_time <- paste0(combined_uema_file$Initial_Prompt_Date, " ", combined_uema_file$Question_Set_Completion_Local_Time)

combined_uema_file$date_timestamp <- as.POSIXct(combined_uema_file$date_time, format="%Y-%m-%d %H:%M:%OS")
```

## Filter dates before june 1 temporarily
For uEMA combined file

```{r}
filter_date <- as.POSIXct("2020-06-01 00:00:00.000", format="%Y-%m-%d %H:%M:%OS")

combined_uema_file <- subset(combined_uema_file, combined_uema_file$date_timestamp >= filter_date)

```

## Remove trivia and val questions
uEMA combined file

```{r}
combined_uema_file <- combined_uema_file[!grepl("Val_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trivia_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trait_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("soc_", combined_uema_file$Question_X_ID),]
```


## Score answers
uEMA combined file

```{r}
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Yes"] <- 3
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Sort of"] <- 2
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "No"] <- 1
# combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "-NOT_ANS-"] <- 0

```


## Create a Q_D column without the numbers
uEMA combined file

```{r}
combined_uema_file$Q_ID <- strsplit(combined_uema_file$Question_X_ID, "[[:digit:]]", perl = TRUE)
combined_uema_file$Q_ID <- lapply(combined_uema_file$Q_ID, '[[', 1)
combined_uema_file$Q_ID <- as.character(combined_uema_file$Q_ID)
combined_uema_file$Q_ID <- gsub(".{1}$", "", combined_uema_file$Q_ID)
```



## Convert sleep wake times in daily report to datetime
Combined daily report file

```{r}

combined_report_df$current_wake_time <- as.POSIXct(combined_report_df$current_wake_time, format="%Y-%m-%d %H:%M:%S")
combined_report_df$current_sleep_time <- as.POSIXct(combined_report_df$current_sleep_time, format="%Y-%m-%d %H:%M:%S")

```

## create a subset for participant
uEMA combined file

```{r}

uEMA_pid_df <- function(df, p_id){
  pid_df <- subset(df, df$Participant_ID == p_id)
  return(pid_df)
}

```

Combined report file
```{r}

report_pid_df <- function(df, p_id){
  pid_df <- subset(df, df$Participant_ID == p_id)
  return(pid_df)
}

```

## Create a subset for the construct
uEMA combined file

```{r}

uEMA_pid_var_df <- function(df, variable){
  var_df <- subset(df, df$Q_ID == variable)
  return(var_df)
}

```




