---
title: "uEMA_burst_ema_comparisons"
author: "Aditya Ponnada"
date: "6/13/2021"
output: html_document
---

# Import library
```{r}

library(ggplot2)
library(plotly)
library(psych)
library(rmcorr)
library(lme4)
library(dplyr)
library(reshape2)
library(cowplot)
library(patchwork)
library(gridExtra)
options(digits = 4)

```

## Read uema trajectories file
```{r}

uema_path <- "D:/new_data_pre_processed/uema_trajectories_combined.csv"

uema_df <- read.csv(file=uema_path, sep = ",", header = TRUE)



```

## Read the burst EMA combined responses + wake period mapped file
```{r}

bema_path = "D:/uema_exploratory_plots/trajectory_plots/bema_merged_df.csv"

bema_df <- read.csv(file=bema_path, sep = ",", header = TRUE)


```

## Create uema_df with only common columns with burst ema
```{r}

uema_comm_df <- uema_df[, c("p_id", "wake_period", "sad", "happy", "fatigue", "energy","relax", "tense", "stress", "frust", "nervous", "focus", "control", "proc", "demands","routine")]

```

## Rename bema columns for consistency
```{r}

names(bema_df) <- c("p_id", "wake_period", "sad", "happy", "fatigue", "energy","relax", "tense", "stress", "frust", "nervous", "focus", "control", "proc","demands","routine")

```


## Remove the "unknown user" account
```{r}

uema_comm_df <- subset(uema_comm_df, uema_comm_df$p_id != "unknown_user")

```

## Keep the same usrs
```{r}

user_list <- unique(uema_comm_df$p_id)

bema_df <- subset(bema_df, bema_df$p_id %in% user_list)

```


```{r}



get_trajectory_freqs <- function(df){
  freq_df <- data.frame()
  col_names <- names(df)
  col_names <- col_names[3:ncol(df)]
  for (col in col_names){
    col_table <- table(df[[col]])
    col_df <- as.data.frame(col_table)
    col_df$var_name <- col
    col_df <- col_df %>% select(var_name, everything())
    freq_df <- rbind(freq_df, col_df)
  }
  
  return(freq_df)
}

```

Now get the df
```{r}
trajectory_dist_uema <- get_trajectory_freqs(uema_comm_df)
trajectory_dist_bema <- get_trajectory_freqs(bema_df)
```


Plot by variable --> heat map
```{r}

get_traj_plot <- function(df, type){
traj_plot <- ggplot(df, aes(x = Var1, y = var_name)) + 
  geom_tile(aes(fill = Freq)) + 
  scale_fill_gradient(name = 'Frequency', low = 'white', high = 'red') + 
  # scale_fill_gradientn(colors = c("white", "red"), values = c(0, 50)) +
  ggtitle("Trajectories vs variables") + 
  ylab(paste0(type, " constructs")) + 
  xlab("Wake period trajectory types") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
return(traj_plot)
}



```

add %days to trajectory_dist
```{r}

get_traj_dist <- function(df){

  df$var_sum_days <- ave(df$Freq, df$var_name, FUN = sum)

  df$perc_days <- df$Freq*100/df$var_sum_days  
  
  return(df)
}



```


Get the traj dist df for bema and uema
```{r}

traj_dist_uema_df <- get_traj_dist(trajectory_dist_uema)
traj_dist_bema_df <- get_traj_dist(trajectory_dist_bema)

```


## Create normalized heat maps for bema and uema
```{r}

get_traj_norm_plot <- function(df, type){
traj_plot <- ggplot(df, aes(x = Var1, y = var_name)) + 
  geom_tile(aes(fill = perc_days)) + 
  # scale_fill_gradient(name = '% days', low = 'white', high = 'red') + 
  scale_fill_gradientn(name = '% days', colors = c("white", "red"), values = scales::rescale(c(0, 50)), limits = c(0, 50)) +
  ggtitle("Trajectories vs variables") + 
  ylab(paste0(type, " constructs")) + 
  xlab("Wake period trajectory types") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
return(traj_plot)
}

```


## Combine the two data frames
```{r}

traj_dist_uema_v2 <- traj_dist_uema_df

names(traj_dist_uema_v2) <- paste0("uema_", names(traj_dist_uema_v2))

traj_dist_bema_v2 <- traj_dist_bema_df

names(traj_dist_bema_v2) <- paste0("bema_", names(traj_dist_bema_v2))

combined_df <- cbind(traj_dist_uema_v2, traj_dist_bema_v2)

```

## Get % days from total measurement days
```{r}

combined_df$bema_total_perc_days <- combined_df$bema_Freq*100/(combined_df$uema_var_sum_days + combined_df$bema_var_sum_days)
combined_df$uema_total_perc_days <- combined_df$uema_Freq*100/(combined_df$uema_var_sum_days + combined_df$bema_var_sum_days)

```

## Get the plot for bema vs uema for the % out of total
```{r}
get_total_perc_plot <- function(df, type){
  if (type == "uEMA"){
    traj_plot <- ggplot(df, aes(x = uema_Var1, y = uema_var_name)) + 
  geom_tile(aes(fill = uema_total_perc_days)) + 
  # scale_fill_gradient(name = '% total days', low = 'white', high = 'red') + 
  scale_fill_gradientn(name = '% total days', colors = c("white", "red"), values = scales::rescale(c(0, 50)), limits = c(0, 30)) +
  ggtitle("Trajectories vs variables") + 
  ylab(paste0(type, " constructs")) + 
  xlab("Wake period trajectory types") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
    
  } else if (type == "Burst EMA") {
    traj_plot <- ggplot(df, aes(x = bema_Var1, y = bema_var_name)) + 
  geom_tile(aes(fill = bema_total_perc_days)) + 
  # scale_fill_gradient(name = '% total days', low = 'white', high = 'red') + 
  scale_fill_gradientn(name = '% total days', colors = c("white", "red"), values = scales::rescale(c(0, 50)), limits = c(0, 30)) +
  ggtitle("Trajectories vs variables") + 
  ylab(paste0(type, " constructs")) + 
  xlab("Wake period trajectory types") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
  }
  
return(traj_plot)
}
```



## Get the difference in % across burst EMA and uEMA
```{r}


traj_dist_uema_df$diff_perc_bema <- traj_dist_bema_df$perc_days - traj_dist_uema_df$perc_days


```

## unction to get the difference plot
```{r}
get_traj_diffperc_plot <- function(df){
  max_diff <- max(df$diff_perc_bema)
  min_diff <- min(df$diff_perc_bema)
traj_plot <- ggplot(df, aes(x = Var1, y = var_name)) + 
  geom_tile(aes(fill = diff_perc_bema)) + 
  # scale_fill_gradient(name = '% diff days', low = 'cyan', high = 'red') + 
  scale_fill_gradientn(colors = c("green", "white", "blue"), values = scales::rescale(c(min_diff, 0, max_diff))) +
  ggtitle("Trajectories vs variables") + 
  ylab(paste0("All", " constructs")) + 
  xlab("Wake period trajectory types") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
return(traj_plot)
}


```

