---
title: "uEMA Vis Prep"
author: "Aditya Ponnada"
date: "1/24/2021"
output: html_document
---
## Include all libraries
Get all the required libraries 

```{r}
library(plotly)
library(ggplot2)
library(shiny)
library(shinycssloaders)
library(shinydashboard)
library(reshape2)
library(dplyr)
library(plyr)
```

## Get file location
Get the root file location and construct user paths from it
```{r}
pre_process_root_path <- "D:/Intermediate_TIME_files/intermediate_file"

file_pattern <- paste0(pre_process_root_path, '/*/*/watch_promptresponse_clean_*.csv')

```


## Combine all the prompt response files for the participant
```{r}
pattern_files_found <- Sys.glob(file_pattern)

combined_uema_file <- do.call(rbind, lapply(pattern_files_found, read.csv))
```

## Convert the prompt time to date time column
```{r}
combined_uema_file <- subset(combined_uema_file, combined_uema_file$Answer_Status == "Completed" | combined_uema_file$Answer_Status == "CompletedThenDismissed" )

combined_uema_file$date_time <- paste0(combined_uema_file$Initial_Prompt_Date, " ", combined_uema_file$Question_Set_Completion_Local_Time)

combined_uema_file$date_timestamp <- as.POSIXct(combined_uema_file$date_time, format="%Y-%m-%d %H:%M:%OS")
```

## Filter dates before june 1 temporarily
```{r}
filter_date <- as.POSIXct("2020-06-01 00:00:00.000", format="%Y-%m-%d %H:%M:%OS")

combined_uema_file <- subset(combined_uema_file, combined_uema_file$date_timestamp >= filter_date)

```

## Remove trivia and val questions
```{r}
combined_uema_file <- combined_uema_file[!grepl("Val_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trivia_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trait_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("soc_", combined_uema_file$Question_X_ID),]
```


## Score answers
```{r}
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Yes"] <- 3
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Sort of"] <- 2
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "No"] <- 1

```

## Question IDs without numbers
```{r}
combined_uema_file$Q_ID <- strsplit(combined_uema_file$Question_X_ID, "[[:digit:]]", perl = TRUE)
combined_uema_file$Q_ID <- lapply(combined_uema_file$Q_ID, '[[', 1)
combined_uema_file$Q_ID <- as.character(combined_uema_file$Q_ID)
combined_uema_file$Q_ID <- gsub(".{1}$", "", combined_uema_file$Q_ID)
```

## Create a function to get participant list
```{r}
get_p_id_list <- function(df){
  p_id_list <- unique(df$Participant_ID)
  return(p_id_list)
}

```


## Create a function to get date list
```{r}

get_date_list <- function(p_id, df){
  p_id_subset <- subset(df, df$Participant_ID == p_id)
  date_list_p_id <- unique(p_id_subset$Initial_Prompt_Date)
  return(date_list_p_id)
}

```


## function to generate start and end times from the date
```{r}
generate_start_end_times <- function(date){
  midnight_past <- "00:00:00.000"
  start_time <- paste0(date, " ", midnight_past)
  start_time <- as.POSIXct(start_time, format = "%Y-%m-%d %H:%M:%OS")
  end_time <- start_time + 24*60*60
  return(list(start_time, end_time))
}

```

## function to generate plot
```{r}
generate_uema_plot <- function(df, p_id, date) {
  start_end_times <- generate_start_end_times(date)
  start_time <- start_end_times[[1]]
  end_time <- start_end_times[[2]]
  
  p_id_subset <- subset(df, df$Participant_ID == p_id)
  p_id_subset <- subset(p_id_subset, p_id_subset$date_timestamp >= start_time & p_id_subset$date_timestamp <= end_time)
  
  day_plot <- ggplot(p_id_subset, aes(x=date_timestamp, y=Answer_score, color=Q_ID)) +
  geom_line() +
  geom_point(size = 2)+
  scale_y_continuous(breaks=seq(1,3,1)) +
  xlim(start_time, end_time) +
  ggtitle(paste0(p_id, " | ", date))

final_plot <- ggplotly(day_plot)
return(final_plot)
}


```



## Function to generate single all time days plot
```{r}

generate_combined_plot <- function(df, p_id, date_list){
  # print(date_list)
  p_id_subset <- subset(df, df$Participant_ID == p_id)
  
  p_id_subset <- subset(p_id_subset, p_id_subset$Initial_Prompt_Date %in% date_list)
  
  combo_plot <- ggplot(p_id_subset, aes(x=date_timestamp, y=Answer_score, color=Q_ID)) +
  geom_line() +
  geom_point(size = 2)+
  scale_y_continuous(breaks=seq(1,3,1)) +
  ggtitle(paste0(p_id, " | ", "TIME days")) +
  facet_grid(.~Initial_Prompt_Date, scale="free_x")
  final_plot <- ggplotly(combo_plot)
  return(final_plot)
}


```



## Generate the p_id list
```{r}
p_id_list <- get_p_id_list(combined_uema_file)
```


## Set up shiny app
```{r}

# Define UI for application that draws a histogram
ui <- fluidPage(
  
  # Application title
  titlePanel("micro-EMA explorer"),
  
  # Sidebar with dropdown
  
  sidebarLayout(
    sidebarPanel(
      # selectInput(inputId = "p_id", choices = p_id_list,
      #             label = "Select date", multiple = FALSE),
      # selectInput(inputId = "date", choices = date_list_p_id,
      #             label = "Select date", multiple = FALSE)
      uiOutput("p_id"),
      uiOutput("date_p_id")
    ),
    # Show a plot of the generated distribution
    mainPanel(
      plotlyOutput("Plot")
    )
    )
  )


server <- function(input, output) {
  
  output$p_id <- renderUI({
        selectInput("p_id", "Select participant", choices = p_id_list)
    })

    ## input dependant on the choices in `data1`
  output$date_p_id <- renderUI({
        selectInput("date_p_id", "Select date", choices = c(get_date_list(input$p_id, combined_uema_file)))
    })
  
  output$Plot <- renderPlotly({
    generate_uema_plot(combined_uema_file, input$p_id, input$date_p_id)
  })
  

}

shinyApp(ui = ui, server = server)

```

## shiny interface for all time days of a single participant
```{r}

# Define UI for application that draws a histogram
ui <- fluidPage(
  
  # Application title
  titlePanel("micro-EMA explorer"),
  
  
  fluidRow(column(4,
                  uiOutput("p_id"),
                  uiOutput("date_p_id"),
                  actionButton("generate_plot", "Show data")
  ),
    
  ),
  hr(),
  plotlyOutput("Plot")
  
  
  # Sidebar with dropdown
  
  # sidebarLayout(position = 'right',
  #   sidebarPanel(
  #     # selectInput(inputId = "p_id", choices = p_id_list,
  #     #             label = "Select date", multiple = FALSE),
  #     # selectInput(inputId = "date", choices = date_list_p_id,
  #     #             label = "Select date", multiple = FALSE)
  #     uiOutput("p_id"),
  #     # uiOutput("date_p_id")
  #   ),
  #   # Show a plot of the generated distribution
  #   mainPanel(
  #     plotlyOutput("Plot")
  #   )
  #   )
  )



server <- function(input, output) {
  
  output$p_id <- renderUI({
        selectInput("p_id", "Select participant", choices = p_id_list)
    })

    ## input dependant on the choices in `data1`
  output$date_p_id <- renderUI({
        selectInput("date_p_id", "Select dates", choices = c(get_date_list(input$p_id, combined_uema_file)), multiple = TRUE)
    })
  
  observeEvent(input$generate_plot, {
    output$Plot <- renderPlotly({
    generate_combined_plot(combined_uema_file, input$p_id, input$date_p_id)
  })
  })
  
  # output$Plot <- renderPlotly({
  #   input$generate_plot
  #   generate_combined_plot(combined_uema_file, input$p_id, input$date_p_id)
  # })
  

}

shinyApp(ui = ui, server = server)

```

