---
title: "Explore uEMA trajectories"
author: "Aditya Ponnada"
date: "4/12/2021"
output: html_document
---

# Include libraries
```{r}
library(lubridate)
library(dplyr)
library(plyr)
library(reshape2)
library(plotly)
library(ggplot2)
library(shiny)
library(shinycssloaders)
library(shinydashboard)
library(psych)

```

# Read the combined uEMA response file

Get the root file location and construct user paths from it
```{r}
# pre_process_root_path <- "D:/Intermediate_TIME_files/intermediate_file"
pre_process_root_path <- "D:/new_data_pre_processed/watch"

# file_pattern <- paste0(pre_process_root_path, '/*/*/watch_promptresponse_clean_*.csv')
file_pattern <- paste0(pre_process_root_path, '/*/watch_promptresponse_clean_*.csv')

```


## Combine all the prompt response files for the participant
```{r}
pattern_files_found <- Sys.glob(file_pattern)

combined_uema_file <- do.call(rbind, lapply(pattern_files_found, read.csv))
```

## Read the combined daily report file
```{r}

combined_report_file = paste0('D:/new_data_pre_processed', '/combined_report_N70.csv')
combined_report_df <- read.csv(combined_report_file, header = TRUE, sep = ',')

```

## Convert the prompt time to date time column
For uEMA combined file

```{r}
combined_uema_file <- subset(combined_uema_file, combined_uema_file$Answer_Status == "Completed" | combined_uema_file$Answer_Status == "CompletedThenDismissed" )
combined_uema_file <- subset(combined_uema_file, combined_uema_file$Question_X_Answer_Text != "-NOT_ANS-")

## if unanswered then set prompt time as the completion time?
# combined_uema_file$Prompt_Time_only <- substr(combined_uema_file$Initial_Prompt_Local_Time, 12, 19)
# combined_uema_file$Question_Set_Completion_Local_Time[combined_uema_file$Question_X_Answer_Text == '-NOT_ANS-'] <- combined_uema_file$Prompt_Time_only


combined_uema_file$date_time <- paste0(combined_uema_file$Initial_Prompt_Date, " ", combined_uema_file$Question_Set_Completion_Local_Time)

combined_uema_file$date_timestamp <- as.POSIXct(combined_uema_file$date_time, format="%Y-%m-%d %H:%M:%OS")
```

## Filter dates before june 1 temporarily
For uEMA combined file

```{r}
filter_date <- as.POSIXct("2020-06-01 00:00:00.000", format="%Y-%m-%d %H:%M:%OS")

combined_uema_file <- subset(combined_uema_file, combined_uema_file$date_timestamp >= filter_date)

```

## Remove trivia and val questions
uEMA combined file

```{r}
combined_uema_file <- combined_uema_file[!grepl("Val_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trivia_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("trait_", combined_uema_file$Question_X_ID),]
combined_uema_file <- combined_uema_file[!grepl("soc_", combined_uema_file$Question_X_ID),]
```


## Score answers
uEMA combined file

```{r}
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Yes"] <- 3
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "Sort of"] <- 2
combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "No"] <- 1
# combined_uema_file$Answer_score[combined_uema_file$Question_X_Answer_Text == "-NOT_ANS-"] <- 0

```


## Create a Q_D column without the numbers
uEMA combined file

```{r}
combined_uema_file$Q_ID <- strsplit(combined_uema_file$Question_X_ID, "[[:digit:]]", perl = TRUE)
combined_uema_file$Q_ID <- lapply(combined_uema_file$Q_ID, '[[', 1)
combined_uema_file$Q_ID <- as.character(combined_uema_file$Q_ID)
combined_uema_file$Q_ID <- gsub(".{1}$", "", combined_uema_file$Q_ID)
```



## Convert sleep wake times in daily report to datetime
Combined daily report file

```{r}

combined_report_df$current_wake_time <- as.POSIXct(combined_report_df$current_wake_time, format="%Y-%m-%d %H:%M:%S")
combined_report_df$current_sleep_time <- as.POSIXct(combined_report_df$current_sleep_time, format="%Y-%m-%d %H:%M:%S")

```

## create a subset for participant
uEMA combined file

```{r}

get_uEMA_pid_df <- function(df, p_id){
  pid_df <- subset(df, df$Participant_ID == p_id)
  return(pid_df)
}

```

Combined report file
```{r}

get_report_pid_df <- function(df, p_id){
  pid_df <- subset(df, df$participant_ID == p_id)
  pid_df <- subset(pid_df, pid_df$study_mode == "TIME")
  return(pid_df)
}

```

## Create a subset for the construct
uEMA combined file

```{r}

get_uEMA_pid_var_df <- function(df, variable){
  var_df <- subset(df, df$Q_ID == variable)
  return(var_df)
}

```

# Test code for a single participant

## get p-id subsets
First for the uEMA combined file

```{r}
participant_id = "sharpnessnextpouch@timestudy_com"

subset_pid_df <- get_uEMA_pid_df(combined_uema_file, participant_id) 
```

Then for the combined daily report file
```{r}

report_pid_df <- get_report_pid_df(combined_report_df, participant_id)

```

## add a waking period column to each response row
```{r}

for(i in 1:nrow(report_pid_df)){
  # print(paste0(i, " _ ", report_pid_df$current_wake_time[i]))
  subset_pid_df$wake_period[subset_pid_df$date_timestamp >= report_pid_df$current_wake_time[i] & subset_pid_df$date_timestamp <= report_pid_df$current_sleep_time[i]] <- paste0("Wake_period_", i)
}

```

## Remove CS microEMA
```{r}
subset_pid_df <- subset(subset_pid_df, subset_pid_df$Q_ID != "activity")
```


## Get a list of relevant construct/variable names
```{r}
var_list <- unique(subset_pid_df$Q_ID)
wake_period_list <- unique(subset_pid_df$wake_period)

```

## Create a slope type function
```{r}

get_slope_type <- function(slist, vlist){
  slope_type = ""
  # print(slist)
  # print(vlist)
  # print(length(unique(vlist)))
  # print(unique(vlist))
  
  if (length(unique(vlist)) == 1){
    if (unique(vlist) == 3){
    slope_type = "Consistent-high"
    } else if (unique(vlist) == 2) {
    slope_type = "Consistent-medium"
    } else if (unique(vlist) == 1){
    slope_type = "Consistent-low"
    }
  } else {
    if (all(diff(slist)) <= 0) {
      slope_type = "Accumulation"
    } else if (all(diff(slist)) >= 0){
      slope_type = "Dissipation"
    } else {
      slope_type = "Fluctuating"
    }
  }
  return(slope_type)
}

```

## Create function to get trajectory
```{r}

get_var_profile <- function(df, variable, wake_period_name){
  wake_subset_df <- subset(df, df$wake_period == wake_period_name & df$Q_ID == variable)
  # wake_subset_df <- subset(wake_subset_df, wake_subset_df$Q_ID == variable)
  # print(wake_subset_df)
  if (nrow(wake_subset_df) != 0){
    slope_list <- c()
    val_list = wake_subset_df$Answer_score
    # print(val_list)
    for (i in 1:nrow(wake_subset_df) - 1){
      del_y <- wake_subset_df$Answer_score[i + 1] - wake_subset_df$Answer_score[i]
      del_x <- as.numeric(difftime(wake_subset_df$date_timestamp[i + 1], wake_subset_df$date_timestamp[i], units = "hours"))
      slope <- del_y/del_x
      slope_list <- c(slope_list, slope)
    }
    profile_type <- get_slope_type(slope_list, val_list)
    return(profile_type)
  } else {
    return(NA)
  }
}

```

## Generate temporal profile for each variable for p_id
```{r}

var_profile_df <- matrix(ncol = length(var_list) + 2, nrow = length(wake_period_list))

for (i in 1:length(wake_period_list)){
  
  var_profile_df[i, 1] <- participant_id
  var_profile_df[i, 2] <- wake_period_list[[i]][1]
  for (j in 1:length(var_list)){
    var_profile_df[i, j + 2] <- get_var_profile(subset_pid_df, var_list[[j]][1], wake_period_list[[i]][1])
  }
  
}

var_profile_df <- as.data.frame(var_profile_df)
col_names <- c("p_id", "wake_period", var_list)

names(var_profile_df) <- col_names

```




